Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-06-25 doc/main_jfm.tex
updates

In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure and the reduced area over the time. Here the enclosed area and the length of the structure are calculated from the midplane. 
These results are shown in Figure~\ref{figure4} where we compare results from a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. 
The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane. Since the starting configuration is close to a circular shape, the reduced are decreases from a value very close to $1$. It is clear that a slower shear rate generates a higher reduced area and has faster convergence. The small oscillations in all results are due to the granular setup of the bilayer which tends to having a slightly non-smooth curve in simulations. Overall the total lengths of the bilayer have the same converging value in all test shear rates. Moreover, based on the 
numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\dot\gamma=0.003$.

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_rupt_0.eps}
\includegraphics[width=0.3\textwidth]{N58_rupt_200.eps}\\
\includegraphics[width=0.3\textwidth]{N58_rupt_400.eps}
\includegraphics[width=0.3\textwidth]{N58_rupt_600.eps}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure7}
\end{figure}

>>>>

In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure and the reduced area over the time. Here the enclosed area and the length of the structure are calculated from the midplane. 
These results are shown in Figure~\ref{figure4} where we compare results from a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. 
The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane. Since the starting configuration is close to a circular shape, the reduced are decreases from a value very close to $1$. It is clear that a slower shear rate generates a higher reduced area and has a faster convergence. The small oscillations in all results are due to the granularity of the bilayer which tend to having a slightly non-smooth curve in simulations. Overall the total lengths of the bilayer have the same converging value in all test shear rates. Moreover, based on the 
numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\dot\gamma=0.003$.

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N58_rupt_0.pdf}
\includegraphics[height=1.2in]{N58_rupt_200.pdf}
\includegraphics[height=1.2in]{N58_rupt_400.pdf}
\includegraphics[height=1.2in]{N58_rupt_600.pdf}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure7}
\end{figure}
